Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as this table shows :

The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey lead us to give up on this. But we still think that should be included in a future research on that topic.

@@

Here, when we mention that an education system reinforces self-confidence, we mean that teachers use positive reinforcement when interacting with students. This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem. This also entails supporting students' taking initiatives, encouraging creativity will also be part of this self-confidence reinforcement.

Ideally we would have also liked to add the social dimension to it, meaning that students that are socially included may have a slightly higher degree of self-confidence, as we saw suggested in the literature.

>>>>

@@

Here, when we mention that an education system reinforces self-confidence, we mean that teachers use positive reinforcement when interacting with students. This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem. This also entails supporting students taking initiatives, encouraging creativity.

The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for. To do so, we will look at average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.

Ideally, since the literature suggests that self-confidence depends partly on one's integration within social networks [@OECD2009], we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too :

The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this. But we still think that should be included in a future research on that topic.

Regarding potential control variables, we should normally consider including at least the main environmental determinants of entrepreneurship but the lack of consistency in the data at hand for our explanatory variables made us use a summary of those as a proxy. We chose to use the level of good opportunities to start a business perceived on average across the population of the given country.

We will now present our quantitative methodology and the indicators we used in greater detail.
